---
title: "hierarchy"
author: "Yanyu Zheng yz2690"
date: "April 9, 2016"
output: html_document
---

## Set up
```{r}
setwd("~/Data Science/project4-team6/lib")
library(igraph)
library(bipartite)
library(intergraph)
library(rPython)
```

## Call python
```{r}
python.load("Recommendation.py")
```

## Read in the graph as adjacency matrix
```{r}
load("matData.RData")
attach(matData)
## Build adjacency matrix
adjMat = matrix(100,nrow=length(levels(uId)),ncol=length(levels(pId)))
colnames(adjMat)=levels(pId)
rownames(adjMat)=levels(uId)
for(i in 1:length(uId)){
  adjMat[uId[i],pId[i]]=score[i]
}
## Save adjacency matrix
save(adjMat,file = "adjMat.RData")
## See the bipartate plot
plotweb(adjMat[1:100,])
playData = adjMat[1:100,]
## Clean up
rm(list = ls())
```

## Recurssively calculating the distance 
```{r}
load("adjMat.RData")
#system.time(computeModules(adjMat,steps=10))
```

## Tryout codes
```{r}
# data = read.csv("datawithnameandgenre.csv")
# attach(data)
# matData = data.frame(product_productid,review_userid,review_score,V1.1)
# colnames(matData) = c("pId","uId","score","name")
# save(matData,file = "matData.RData")

# g <- make_empty_graph() +
#                  vertices(letters[1:10]) +
#                  vertices("foo", "bar", "bar2", "foobar2")
#           g <- g + edge("a", "b",weight = 3)
# 
# as.matrix.igraph(g,matrix.type = "adjacency")         
sampledata <- rbind(
    c(1,2,4),
    c(1,3,2),
    c(2,1,4),
    c(2,3,4),
    c(2,4,1),
    c(2,5,2),
    c(3,1,2),
    c(3,2,4),
    c(4,2,1),
    c(5,2,2),
    c(5,6,1),
    c(6,5,1))
# playdata = cbind(data$product_productid,data$review_userid,data$review_score)[1:500,]
# system.time(adjMat = frame2webs(matData,varnames = c("uId","pId","score")))
data(Safariland)
plotweb(Safariland)
clustering_tm(Safariland)
compart(Safariland)
fc(Safariland)
fc(playData)
computeModules()

data(small1976)
res <- computeModules(small1976)
plotModuleWeb(res)

```

## Summary of a few clustring methods

### computeModules from packages Bipartite
```{r }
computeModules()
```

Pros: 1 Comes from a package specialized bipartite graphs. So the algorithm is modified to suit "higher species" and "lower species".
      2 Easily find the among-module connectivity using czvalue() after computing the modules.
      
Cons: Way tooooooo slow. Can't even finish the calculation for 10 iterations without killing my computer. (default is 1000000 iterations)

